Analyzing DECREASE trials for extent of data fabrication

### 2016-03-09 submission/manuscript.Rmd
Update markdown file with ln(odds) computation

where *n* is the total amount of data points in that condition. This results in four estimates:

@@

1. Take the entire sample from one DECREASE study, with the prespecified group sizes from that DECREASE study (e.g., 49 controls and 51 patients on beta-blockers). 
2. Randomly assign X={0, 1, 2, … , N} of the data points to be faked. 
3. Draw an ln(odds) from the corresponding population effect 1-4 outlined above. 
4. Sample an event with the probability calculated from the ln(odds) from the previous step and note the data point 0 (no event) or 1 (event) from either the genuine effect distribution (estimates 1 + 2), or faked effect distribution (estimates 3 + 4). 
5. When all data points have been generated, estimate the ln(RR) in this simulated sample with metafor and REML estimation.
6. Note whether this ln(RR) is more likely under the non-DECREASE effect distribution (coded 0) or under the DECREASE effect distribution (coded 1), based on two-sided p-values (larger p-value is more probable)
7. Repeat k times (k = number of iterations)
8. Calculate proportions of iterations where estimate was more likely under fabrication than under genuine data.
9. Note for how many data points from the fabricated (DECREASE) distribution the proportion is closest to .025 and .975 to provide a 95% confidence interval of data points fabricated

>>>>

where *n* is the total amount of data points in that condition. In the case that no events occurred in the condition and *p* = 0, *p* is calculated as for example

$p=\frac{c+.5}{a+c+.5}$

where a and c are indicated in Table 1. This adjustment prevents computational errors and introduces minimal bias [@agresti2002].

These meta-analyses result in four estimates:

@@

1. Take the entire sample from one DECREASE study, with the prespecified group sizes from that DECREASE study (e.g., 49 controls and 51 patients on beta-blockers). 
2. Randomly assign X={0, 1, 2, … , N} of the data points to be faked. 
3. Draw an ln(odds) from the corresponding population effect 1-4 outlined above. 
4. Sample an event with the probability calculated from the ln(odds) from the previous step and note the data point 0 (no event) or 1 (event) from either the genuine effect distribution (estimates 1 + 2), or faked effect distribution (estimates 3 + 4). 
5. When all data points have been generated, estimate the ln(RR) in this simulated sample with `metafor` and REML estimation.
6. Note whether this ln(RR) is more likely under the non-DECREASE effect distribution (coded 0) or under the DECREASE effect distribution (coded 1), based on two-sided p-values (larger p-value is more probable)
7. Repeat k times (k = number of iterations)
8. Calculate proportions of iterations where estimate was more likely under fabrication than under genuine data.
9. Note for how many data points from the fabricated (DECREASE) distribution the proportion is closest to .025 and .975 to provide a 95% confidence interval of data points fabricated
